plot

### 2024-11-29 effects_lba_summary.Rmd
added wrangle, model and effects .Rmd files

I made a plot like this recently to summarise Raph's results.

Eventually, we could add the rt dist for acc/inc in the raw data below, as we did for Raph's data.

@@

## load packages ##

@@

## plot settings ##

@@

## load the model object and/or data ##

```{r}
## The model object is available upon request
## Please email Samantha Parker (samantha.parker@students.mq.edu.au) or Richard Ramsey (richard.ramsey@hest.ethz.ch)
## load("models/modelKN.RData") ##  
load_model ("LBA","lba_B.R")
```

# section 1 - posterior predictions #

@@

@@

## you could save a figure at this point, if you wanted
ggsave("figures/ppreds.jpeg",
       width = 10, height = 8)
```

# section 2 #

## what about visualising parameters from the model? ##

@@

Note to Raph/Sam and a reminder for Rich: One thing that took a little (or rather a lot of) figuring out was how the DMC compare.p convenience function calculates group average parameter estimates for the posterior distribution. It takes all pid posteriors, averages them first and then calculates the relevant quantiles to display and make inferences from. In other words, it first summarises parameters over pid 1, 2, 3, etc. and then calculates quantiles. This matters, because you could also calculate the quantiles without first averaging. So, the below has been tested to produce the same outputs as the compare.p function, which is re-assuring.

@@

ggsave("figures/all_params.jpeg",
       width = 8, height = 6)
```

@@

```{r}
p2.2 <- ggplot(theta_group, aes(x = value, y = fct_rev(param))) +  
  stat_halfeye(alpha = 0.9, position = position_nudge(y=-0.5)) +
  geom_pointinterval(data = theta_pid_q, aes(xmin=.lower, xmax=.upper, 
                                           colour = pid, fill = pid),
                     position = position_dodge(width = 0.7)) +
  labs(x = "parameter estimate", y = "") +
  facet_wrap(~param, scales = "free_y") +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
p2.2

ggsave("figures/all_params_pid.jpeg",
       width = 10, height = 10)
```

Ok, at this point, we could wrangle the data and make some nice plots.
For code on how to do this, see folder /pilot5_dmc/ in Raph's project.
But Sam has already done that using the compare.p function and so there is no real need to reproduce those.
Instead, we should try to move on to visualise the average parameter estimates from the model in a LBA model type way.  
For that, we only need the average estimates per parameter, which we calculated above already.

# Section 3 - make a plot to visualise the results in LBA model format? ##

@@

e.g., take the raw data and make density dists, then plot alongside the parameters but in model format, rather than posterior distributions?

@@

This plot could just characterise/visualise the main results in a LBA schematic kind
of way. 
And that way may be more intuitive and provide an overview for readers of the main findings.

@@

ggsave("figures/lba_summary.jpeg",
       width = 8, height = 5, dpi=800)
```

How about we try to add rt and acc desnity plots like we did before with Raph's data?

# Section 4 #

@@

## summary data ##

@@

@@

@@

ggsave("figures/density_rt_acc.jpeg",
       width = 12, height = 8, dpi=800)
```

@@

ggsave("figures/lba_rt_acc.jpeg",
       width = 12, height = 10, dpi=800)
```

>>>>

@@

@@

# plot settings #

@@

# load the model object #

```{r}
## The model object is available upon request
## Please email Samantha Parker (samantha.parker@students.mq.edu.au) or Richard Ramsey (richard.ramsey@hest.ethz.ch)
load("models/ea/modelKN.RData") ##  
load_model ("LBA","lba_B.R")
```

# 1. posterior predictions #

@@

This might take 30 seconds or so...

@@

## you could save a figure at this point, if you wanted
ggsave("figures/ea/ppreds_fit.jpeg",
       width = 10, height = 8, dpi = 800)
```

# 2. visualise parameters from the model ##

@@

Note to Sam and a reminder for Rich: One thing that took a little (or rather a lot of) figuring out was how the DMC compare.p convenience function calculates group average parameter estimates for the posterior distribution. It takes all pid posteriors, averages them first and then calculates the relevant quantiles to display and make inferences from. In other words, it first summarises parameters over pid 1, 2, 3, etc. and then calculates quantiles. This matters, because you could also calculate the quantiles without first averaging. So, the below has been tested to produce the same outputs as the compare.p function, which is re-assuring.

@@

# ggsave("figures/ea/all_params.jpeg",
#        width = 8, height = 6)
```

@@

```{r}
p2.2 <- ggplot(theta_group, aes(x = value, y = fct_rev(param))) +  
  stat_halfeye(alpha = 0.9, position = position_nudge(y=-0.5)) +
  geom_pointinterval(data = theta_pid_q, aes(xmin=.lower, xmax=.upper, 
                                           colour = pid, fill = pid),
                     position = position_dodge(width = 0.7)) +
  labs(x = "parameter estimate", y = "") +
  facet_wrap(~param, scales = "free_y") +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
p2.2
# ggsave("figures/all_params_pid.jpeg",
#        width = 10, height = 10)
```

Ok, at this point, we could wrangle the data further and make some nice plots.
But Sam has already done that using the compare.p function and so there is no real need to reproduce those.

Instead, we will try to move on to visualise the average parameter estimates from the model in a LBA model type way.  
For that, we only need the average estimates per parameter, which we calculated above already.

# 3. make a plot to visualise the results in LBA model format ##

@@

@@

This plot could just characterise/visualise the main results in a LBA schematic kind
of way. 
And by doing so, it may be more intuitive and provide an overview for readers of the main findings.
However, the main conclusions will stem from the formal analysis of the posterior distribution (see effects_lba.Rmd for details).

@@

ggsave("figures/ea/lba_summary.jpeg",
       width = 8, height = 5, dpi=800)
```

# 4. How about we try to add rt and acc density plots? #

@@

@@

accuracy

@@

rt

@@

ggsave("figures/ea/density_rt_acc.jpeg",
       width = 12, height = 8, dpi=800)
```

@@

ggsave("figures/ea/lba_rt_acc.jpeg",
       width = 12, height = 10, dpi=800)
```
